Results MSRC latent class analysis

### 2021-02-15 manuscript/manuscript.Rmd
Add explanation for dichotomization

>>>>

We present descriptive statistics of the observed variables below (see Table \@ref(tab:tabdesc)).
Two of the latent class indicators,
NSSI history and suicide attempt frequency,
were measured at a continuous level of measurement.
However, these variables were censored and positively skewed in the extreme,
such that $`r round(100*prop.table(table(df[["CDE13"]]))[1])`\%$ of participants reported the lowest level of NSSI, and $`r round(100*prop.table(table(df[["CDE17"]]))[1])`\%$ of participants reported the lowest level of suicide attempts.
Based on a visual comparison of transformations for skewed variables (square root, log, inverse, rank-ordering, and median dichotomization),
it was observed that most transformations split the sample into this lowest category versus all other response levels.
This indicates that, despite the continuous measurement scale, these variables convey information at the binary level.
We thus used median dichotomization to account for the deviation from normality,
and treated these dichotomized variables as ordinal.
This is a validated approach for dealing with severely censored variables (Muthén & Speckart, 1983).

```{r tabdesc, results = "asis"}
knitr::kable(desc, caption = "Descriptive statistics")
```
